The Right Way to Search Evolving Graphs

### 2016-02-20 paper.tex
more analysis of algebraic BFS
update experiments

@@

To study evolving graphs and experiment with various graph types, we have
developed EvolvingGraphs.jl~\cite{zhang15}, a software package for the creation,
manipulation, and study of evolving graphs written in Julia~\cite{bkse12}.
It is freely available online at
\begin{center}
\url{https://github.com/weijianzhang/EvolvingGraphs.jl}
\end{center}
and available with the MIT ``Expat'' license. The package contains an implementation
of the evolving graph BFS. \texttt{IntEvolvingGraph}, a data type in EvolvingGraphs.jl,
represents an evolving graph as adjacency lists.
We generate a group of  random (directed) \texttt{IntEvolvingGraph}s with $2000$ nodes and $4$ time stamps, where each edge is included in the graph with
probability $p$.
 Figure \ref{fig:time} shows the plots of  number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted 
in a Linux system with Intel(R) Core(TM) i7-3537U CPU @ $2.00$GHz.
The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with Theorem \ref{thm:complexity}. A summary of the experiments is provided in Table \ref{tab:bfs}.
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.44]{time.png}
  \caption{Experiments of computing Algorithm \ref{alg:bfs} on a group of 
random evolving 
graphs with $2000$ nodes and $4$ time stamps. The x-axis shows the 
number of edges of each evolving graph and the y-axis shows the corresponding
computation time. The values in the x, y-axis increase linearly from left to 
right and from bottom to top respectively.}
  \label{fig:time}
\end{figure}
\begin{table}[h]
\centering
\begin{tabular}{c | c | c | c }
\hline
probability $p$ & no. of edges  & time (s) &  memory (MB) \\\hline
      0.01  &         160,156      & 0.098   & 18.388  \\
      0.09  &       1,440,895        & 0.446  &  134.253  \\
      0.15   &     2,399,774         & 0.743 & 221.511 \\
      0.23   &    3,676,959          & 1.206 &   337.688 \\
      0.31   &     4,956,969          & 1.504  &  494.833 \\
\end{tabular}
\caption{the computation time and the amount of memory allocated for 
computing Algorithm \ref{alg:bfs} on a random evolving graph represented 
adjacency lists with $4$ time stamps and $2000$ nodes.  
Each edge is included in the graph with probability $p$. 
This is a summery of Figure \ref{fig:time}.}
\label{tab:bfs}
\end{table}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.

>>>>

If $\bm A_n$ is sparse, forming $\bm A_n$ costs $\Theta(|E|)$ flops. 
The gaxpy operation in line $7$ costs 
$2m$ flops, where $m$ is the number of none zeros of $\bm A_n$ \cite[Sec.11]{golo13}. 
Here $m$ is equal to $|E|$. Thus, in the worst case, the total running time is 
$\Theta(|E|^2)$.

% Storing $\bm A_n$ requires $\Theta(|V|^2)$ memory and if $\bm A_n$ is sparse, 
% we need $O(|V|+|E|)$ memory.

@@

To study evolving graphs and experiment with various graph types, we have
developed EvolvingGraphs.jl~\cite{zhang15}, a software package for the creation,
manipulation, and study of evolving graphs written in Julia~\cite{bkse12}.
It is freely available online at
\begin{center}
\url{https://github.com/weijianzhang/EvolvingGraphs.jl}
\end{center}
and available with the MIT ``Expat'' license. The package contains an implementation
of the evolving graph BFS. \texttt{IntEvolvingGraph}, a data type in EvolvingGraphs.jl,
represents an evolving graph as adjacency lists.
We generate a group of  random (directed) \texttt{IntEvolvingGraph}s with $8,000$ active nodes and $4$ time stamps, where each edge is included in the graph with
probability $p$.
 Figure \ref{fig:time} shows the plots of  number of edges against the computation time
for running Algorithm \ref{alg:bfs}
in Julia. All experiments are conducted 
in a Linux system with Intel(R) Core(TM) i7-3537U CPU @ $2.00$GHz.
The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with Theorem \ref{thm:complexity}. A summary of the experiments is provided in Table \ref{tab:bfs}.
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.44]{time.png}
  \caption{Experiments of running Algorithm \ref{alg:bfs}
on a group of random evolving graphs with $8,000$ active nodes and $4$ time stamps. The x-axis shows the
number of edges of each evolving graph and the y-axis shows the corresponding
computation time. The values in the x, y-axis increase linearly from left to 
right and from bottom to top respectively.}
  \label{fig:time}
\end{figure}
\begin{table}[h]
\centering
\begin{tabular}{c | c | c | c }
\hline
probability $p$ & no. of edges  & time (s) &  memory (MB) \\\hline
      0.01  &         160,156      & 0.098   & 18.388  \\
      0.09  &       1,440,895        & 0.446  &  134.253  \\
      0.15   &     2,399,774         & 0.743 & 221.511 \\
      0.23   &    3,676,959          & 1.206 &   337.688 \\
      0.31   &     4,956,969          & 1.504  &  494.833 \\
\end{tabular}
\caption{the computation time and the amount of memory allocated for 
computing Algorithm \ref{alg:bfs}. This is a summery of Figure \ref{fig:time}.  
Each edge is included in the graph with probability $p$. }
\label{tab:bfs}
\end{table}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.
